Type-Safe Modular Parsing

### 2017-06-08 SLE_17/sections/Introduction.tex
deleted one paragraph

Syntactic modularization techniques have also been applied to the
problem of \emph{extensible parsing}. Many parser
generators~\cite{antlr1995,Grimm2006,Gouseti2014,Warth2016} support
modular grammars. For instance, \textit{Rats!}~\cite{Grimm2006} has
its own module system for the collection of grammars.  Extensible
compilers like JastAdd~\cite{Ekman2007} and
Polyglot~\cite{Nystrom2003} also support extensible parsing, but this
is mostly done ultimately resorting to standard (non-modular) parser
generators. Various techniques supporting languages that can extend
their own syntax, such as SugarJ~\cite{Erdweg2011}, also offer a form
of extensible parsing. However those syntactic approaches do not
support separate compilation and/or modular type-checking
of parsing code either.

@@

So far research on semantic modularization techniques has focused on
operations that \emph{traverse} or \emph{process} extensible
data structures, such as ASTs. Indeed many documented applications of
semantic modularization techniques focus on modularizing various
aspects of PL implementations.  However, as far as we know, there is
little work on operations that build/produce ASTs.  In particular the
problem of how to modularize parsing has not been studied in semantic
modularization approaches. At best, techniques such as NOA~\cite{Gouseti2014}
employ a syntactic modularity approach for parsing in combination with
a semantic modularity approach for defining operations
that traverse or process ASTs. This is a shame because parsing is a
fundamental part of PL implementations, and it ought to be made
semantically modular as well, so that the full benefits of semantic
modularity apply.

@@

\item \textbf{TAPL case study:} We conduct a case study with 18 interpreters
  from the TAPL book. The case study show the effectiveness of modular
  parsing in terms of reuse. The TAPL case study is available online
  at:
  \url{http://}\bruno{Please add the link here!}

>>>>

\begin{comment}
Syntactic modularization techniques have also been applied to the
problem of \emph{extensible parsing}. Many parser
generators~\cite{antlr1995,Grimm2006,Gouseti2014,Warth2016} support
modular grammars. For instance, \textit{Rats!}~\cite{Grimm2006} has
its own module system for the collection of grammars.  Extensible
compilers like JastAdd~\cite{Ekman2007} and
Polyglot~\cite{Nystrom2003} also support extensible parsing, but this
is mostly done ultimately resorting to standard (non-modular) parser
generators. Various techniques supporting languages that can extend
their own syntax, such as SugarJ~\cite{Erdweg2011}, also offer a form
of extensible parsing. However those syntactic approaches do not
support separate compilation and/or modular type-checking
of parsing code either.
\end{comment}

@@

So far research on semantic modularization techniques has focused on
operations that \emph{traverse} or \emph{process} extensible
data structures, such as ASTs. Indeed many documented applications of
semantic modularization techniques focus on modularizing various
aspects of PL implementations.  However, as far as we know, there is
little work on operations that build/produce ASTs.  In particular the
problem of how to modularize parsing has not been studied in semantic
modularization approaches. Techniques such as NOA~\cite{Gouseti2014}
employ a syntactic modularity approach for parsing in combination with
a semantic modularity approach for defining operations
that traverse or process ASTs. This is a shame because parsing is a
fundamental part of PL implementations, and it ought to be made
semantically modular as well, so that the full benefits of semantic
modularity apply.

@@

\item \textbf{TAPL case study:} We conduct a case study with 18 interpreters
  from the TAPL book. The case study show the effectiveness of modular
  parsing in terms of reuse. The TAPL case study is available online
  at:
  \url{https://github.com/lihuanglx/modular-parsing}
